### 2014-03-16 src/analysis.Rnw
Shortening table description a little bit
Correct the labels in graphs

Next, for each criteria, we computed the reduction of mutants given by the
ratio between total number of mutants and sampled mutants.
We also compute standard deviation of the mutant reduction, which determines
the consistency of results. A large standard deviation suggests
that the mutant reduction ratio achieved is very much dependent on the
project. Therefore, as a heuristic, we suggest looking at only those methods which
have a mean reduction ratio at least twice the standard deviation.

@@

df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)
df$sqr <- 1 - df$r.square
df$mult <- 1 - df$score.multiplier
df$type <- with(df, as.factor(
      ifelse(grepl('line',operator), 'line',
        ifelse(grepl('block',operator), 'block',
        ifelse(grepl('method',operator), 'method',
          ifelse(grepl('class',operator), 'class',
            ifelse(grepl('project',operator), 'project',
              ifelse(grepl('per_op',operator), 'x% operator',
              'operator selection'))))))))
df$sampling <- with(df,
          ifelse(grepl('onelement',strategy), 'one(x)',
            ifelse(grepl('locelement',strategy), 'lines(x)',
              ifelse(grepl('withinelement',strategy), 'one(x)',
                ifelse(grepl('xceilperunit',strategy), 'ceil(x)',
                  ifelse(grepl('xpercentperunit',strategy), 'round(x)',
                    ifelse(grepl('xprobperunit',strategy), 'sample(x)',
'other')))))))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type)) + myopts
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type)) + myopts
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\label{fig:fullimgsize}
\end{figure*}

>>>>

Next, for each criteria, we computed the reduction of mutants given by the
ratio between sampled mutants and total number of mutants.
We also compute standard deviation of the mutant reduction, which determines
the consistency of results. A large standard deviation suggests
that the mutant reduction ratio achieved is very much dependent on the
project. Therefore, as a heuristic, we suggest looking at only those methods which
have a mean reduction ratio at least twice the standard deviation.

@@

df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)
df$sqr <- 1 - df$r.square
df$mult <- 1 - df$score.multiplier
df$type <- with(df, as.factor(
      ifelse(grepl('line',operator), 'line',
        ifelse(grepl('block',operator), 'block',
        ifelse(grepl('method',operator), 'method',
          ifelse(grepl('class',operator), 'class',
            ifelse(grepl('project',operator), 'project',
              ifelse(grepl('per_op',operator), 'x% operator',
              'operator selection'))))))))
df$sampling <- with(df,
          ifelse(grepl('onelement',strategy), 'one(x)',
            ifelse(grepl('locelement',strategy), 'lines(x)',
              ifelse(grepl('withinelement',strategy), 'one(x)',
                ifelse(grepl('xceilperunit',strategy), 'ceil(x)',
                  ifelse(grepl('xpercentperunit',strategy), 'round(x)',
                    ifelse(grepl('xprobperunit',strategy), 'sample(x)',
'other')))))))

df$type <- factor(df$type, levels=c('block','line','method','class','project','x% operator','operator selection'))

ggplot(df, aes(mutant.reduction, sd.reduction)) +
   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
   geom_point(aes(size=sqr, color=type)) + myopts
ggplot(df, aes(mutant.reduction, sd.reduction)) +
   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
   geom_point(aes(shape=sampling, color=type)) + myopts
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\label{fig:fullimgsize}
\end{figure*}
